Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-03-24 tex/paper1/paper1.tex
small changes to paper
filling in some plots

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\slugcomment{Not to appear in Nonlearned J., 45.}

@@

\shorttitle{Collapsed Cores in Globular Clusters}
\shortauthors{Djorgovski et al.}

@@

\title{Power law properties of Fourier power spectra and their
  implications for coronal seismology and coronal heating.}

@@

\begin{figure}
\label{fig:loc171}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_171.eps}
\caption{171 and 193}
\end{figure}

@@

\begin{figure}
\label{fig:dist171}

\begin{figure}
\label{fig:dist193}

@@

\begin{figure}
\label{fig:geom171}

\begin{figure}
\label{fig:geom193}

>>>>

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jack.ireland@nasa.gov}

@@

%\slugcomment{Not to appear in Nonlearned J., 45.}

@@

\shorttitle{Properties of coronal Fourier power spectra}
\shortauthors{Ireland et al.}

@@

\title{Properties of coronal Fourier power spectra and their
  implications for coronal seismology and coronal heating.}

@@

\begin{figure}
\label{fig:loc171}
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.}
\end{figure}

@@

\begin{figure}
\label{fig:dist171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.}
\end{figure}

\begin{figure}
\label{fig:dist193}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see Figure \ref{fig:dist171}.)}
\end{figure}

@@

\begin{figure}
\label{fig:geom171}
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.geometric_mean_power_spectra.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
\caption{}
\end{figure}

\begin{figure}
\label{fig:geom193}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.geometric_mean_power_spectra.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
